---
title: "p8105 homework 5"
author: "Xintao Ding"
date: "11/9/2019"
output: github_document
---


```{r setup, include=FALSE}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

```


## Problem 1 
write a function that takes a vector as an argument; replaces missing values using the rules defined above; and returns the resulting vector;apply this function to the columns of iris_with_missing using a map statement
```{r}
set.seed(10)
iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))

#define a function
missing_values_replacement = function(x) {
  if(is.numeric(x)) {
    replace(x, is.na(x), mean(x, na.rm = TRUE)) #replace numeric missing values with mean 
  } else if (is.character(x)) {
    replace(x, is.na(x), "virginica")   #replace character missing values with a certain word
}
  }

iris_withnot_missing = map_dfr(iris_with_missing, missing_values_replacement) # map the function to iris_with_missing
iris_withnot_missing
```

## Problem 2

```{r message = FALSE, warning = FALSE}
# create a dataframe with list file names
file_name <- list.files("./data") 
df <- tibble(file_name)
df <- df %>% 
  mutate(outcome = map(file_name, ~read_csv(str_c("./data/", .x)))) # iterate file names and save as a new variable
df

# tidy data frame
tidy_df <- df %>% 
  separate(file_name, into = c("arm", "subject_id"), sep = "_") %>% 
  mutate (subject_id = gsub("\\.csv", "", subject_id)) %>%  # include subject ID
  unnest() %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to = "outcome"
  )
  
tidy_df

# plotting
plot <- tidy_df %>% 
  ggplot(aes(x = week, y = outcome, group = subject_id, color = subject_id)) +
  geom_line() +
  facet_grid(~arm) +
  labs(title = "Observatinos on Each Subject over Time")
plot
```
Subjects in control arm have overall lower outcomes than those of subjects in the experimental arm. Subjects in the experimantal arm also see a bigger variance in outcome over 8 weeks, whereas subjects in the control arm have outcomes that do not fluctuate much over the 8 week course. 

##Problem 3
```{r message = FALSE, warning = FALSE}

set.seed(1)
sim_regression = function(n = 30, beta0 = 2, beta1){
  sim_data = tibble (
    x = rnorm(n, mean = 0, sd = 1),
    y = beta0 + beta1 * x + rnorm(n, 0, sd = sqrt(50))
  )
  ls_fit <-  lm(y ~ x, data = sim_data) %>% 
    broom::tidy() 
  
tibble(
    beta1_hat = ls_fit[[2,2]],
    beta1_p = ls_fit [[2,5]]
    )    
  
}

output <-  rerun(10000, sim_regression(beta1 = 0)) %>% 
  bind_rows()
output

# when β1={1,2,3,4,5,6}
sim_results <- tibble(beta_1 = c(1,2,3,4,5,6)) %>% 
  mutate(output_list = map(.x = beta_1, ~rerun(10000, sim_regression(beta1= .x))),
         output_df = map(output_list, bind_rows))%>%
  select(-output_list) %>% 
  unnest(output_df)

head(sim_results)

# Plotting
sim_results %>% 
  mutate(reject_null = ifelse(beta1_p <= 0.05, 1,0))%>% 
  group_by(beta_1) %>% 
  summarise(power = mean(reject_null)) %>%  #proportion of time null is rejected
  ggplot(aes(x = beta_1, y = power)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = "Association between Beta 1 and Power")
  
```

We can see that as effect size increases, power increases

```{r}
# Plotting
sim_results %>% 
  group_by(beta_1) %>% 
  summarize(avg_beta1_hat = mean(beta1_hat)) %>% 
  ggplot(aes(x = beta_1, y = avg_beta1_hat)) + 
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = "Association between Beta 1 and Average Beta 1 hat", 
       x = "True Beta 1", 
       y = "Average Beta 1 Hat")

sim_results %>% 
  mutate(reject_null = ifelse(beta1_p <= 0.05, 1,0)) %>% 
  filter(reject_null == 1) %>% 
  group_by(beta_1) %>%
  summarise(avg_beta1_hat = mean(beta1_hat)) %>% 
  ggplot(aes(x = beta_1, y = avg_beta1_hat)) +
  geom_point() +
  geom_smooth(se = FALSE) + 
  labs(title = "Assocation between Beta 1 and Average Beta 1 Hat that Reject Null", 
      x = "True Beta 1", 
      y = "Average Beta 1 Hat")
  
  
  
```
We can see from the first graph that the true beta 1 values and average estimated beta 1 values are approximately the same. However, when we look at the second graph, when the null hypothesis is rejected, average estimated beta 1 values are not as close in value to true beta 1. 
